Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-06-15 completeness.tex
touches on completeness

On the other hand, The completeness magnitude, denoted as $M_c$, is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period. While the year of completeness can be determined by inspection of the data, the completeness magnitude often requires a numerical analysis of the catalog. A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve. This method is widely used and has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}. \citet{Zare2014}, for instance, used this method to identify $M_c$ values for the different regions of the Middle East.

>>>>

On the other hand, the completeness magnitude---denoted as $M_c$---is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period. While the year of completeness can be determined by inspection of the data, the completeness magnitude often requires a numerical analysis of the catalog. A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve. This method is known as the maximum curvature (MAXC) technique. It is widely used and has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}. \citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.

### 2016-06-15 parameters.tex
touches on completeness

Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3). This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}. HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{}\textcolor{red}{[references needed]}.

>>>>

Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3). This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}. HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{Karimiparidari2013, Khodaverdian_2016_BSSA}.
